### 2020-12-22 fe_px_paper/fe_body_text.tex
Adding Fe paper pre-PU changes

        \subfigimg[width=0.485\textwidth]{b)}{./figures/after_minimization_plot_alt.pdf}{50}
         %         \refstepcounter{subfigure}
         \label{fig:fe_after_minimization}
   \hspace{-5pt}}%
    \caption{Proton fluence at various positions in both the 55\,MeV and 25\,MeV target stacks as determined by the Ti and Cu monitor foils before (left) and after (right) variance minimization. Open data points represent the 25\,MeV stack, and filled data points represent the 55\,MeV stack. The abrupt change in the post-minimization value at the energies where the two stacks overlap can be attributed to the to the relatively large energy straggle at the back of the high energy stack.}  
%     Results of variance minimization through increasing the effective areal density of the  aluminum degraders by 4.43\% (55\,MeV stack) and Kapton tape by 5.69\% (25\,MeV stack). A noticeable reduction of variance in measured proton fluence is seen,  particularly at the  rear stack positions.  Open data points represent the 25\,MeV stack, and filled data points represent the 55\,MeV stack.} 
     \label{fig:fe_variance_mins}
\end{figure*}

@@

In addition to the \ce{^{nat}Fe}(p,x)\ce{^{51,52}Mn} measurements, this experiment has also yielded production cross section  measurements of  a number of additional  emerging radionuclides with medical applications,
including the non-standard positron emitter 
% \ce{^{44}Sc}\,\cite{Muller2013,Filosofov2010,Qaim2011}
%\,\cite{Qaim2011,Qaim201731,Kolsky1998,mausner1995evaluation}.
\ce{^{55}Co}\,\cite{Thisgaard2011,Zaman1996,Hermanne2000a}.
% \ce{^{61}Ni}\,\cite{PMID:7632762,zweit1996medium,Graves2016,Rosch2014}, 
% \ce{^{61}Cu}\,\cite{Szelecsenyi2005a,Fukumura2004}
% \ce{^{64}Cu}\,\cite{Lewis2003,Bandari2014,mp500671j,Szelecsenyi1993,Aslam2009,Hilgers2003,Szelecsenyi2005,Voyles2017},
% \ce{^{86}Y}\,\cite{Valdovinos2017,Nickles2003,Qaim2008,QaimSyedM2011,Rosch1993,doi:10.1139/v67-193,levkovski1991cross,Johnson2015,Singh2013,Kiselev1974,Kandil2009}, 
% \ce{^{89}Zr}\,\cite{Verel2003,Dijkers2009,Dijkers2010,PhysRevC.38.1624,Omara2009},  
% \ce{^{90}Nb}\,\cite{Busse2002,Radchenko2012},  
% the $\beta^-$-therapy agent  \ce{^{64}Cu},  
% and the $\beta^-$-therapeutic agent 
% \ce{^{47}Sc}\,\cite{Muller2014,Deilami-nezhad2016}.
% and the Auger-therapy agent \ce{^{82\text{m}}Rb}\,\cite{Kovacs1991,Titarenko2011}. 
Production of this radionuclide offerss no major advantages over established pathways, with the  lower yield and radioisotopic purity failing to justify the convenience of natural targets  via   \ce{^{nat}Fe}(p,x).
The one potential exception to this is the production of \ce{^{58m}Co}, a potent agent for Auger electron-based targeted therapy\,\cite{Thisgaard2011a,Valdovinos2017b,Thisgaard2014a}.
While ingrowth of the long-lived \ce{^{58g}Co} ($t_{1/2}$ = 70.86(6) d\,\cite{Nesaraja2010}) is unavoidable, lowering the  co-production of \ce{^{58g}Co} is necessary to minimize patient dose.
The \ce{^{nat}Fe}(p,x)\ce{^{58m}Co} pathway shows a clear \enquote{peak} in the \ce{^{58m}Co}/\ce{^{58g}Co} branching ratio for approximately 15--30\,MeV protons, which might have translational implications if Auger electron therapy becomes more clinically prevalent.

@@

% Perhaps due to the abundance of reaction data available, 
The modeling of these channels is markedly improved  in comparison to the \ce{^{nat}Fe}(p,x) channels discussed previously.
For \ce{^{44m}Sc}, 
% the shape of the excitation function is well-modeled by EMPIRE, CoH, TALYS, and TENDL, though 
all  codes place the compound peak approximately 4\,MeV lower than observed, and EMPIRE overestimates the magnitude of this peak, while TALYS, TENDL, and CoH significantly underestimate it.
Notably, the pre-equilibrium tail and transition towards a second peak near 65\,MeV is well-modeled by TALYS/TENDL, but signficantly underestimated by EMPIRE and CoH.
The same modeling trend is observed for \ce{^{44m}Sc}, 
% though no judgment can be made for the pre-equilibrium tail, due to a paucity of data above 50\,MeV.
and reflected in the measured isomer branching ratios for \ce{^{44}Sc}, seen in \autoref{fig:44Sc_IBR}.
Above 23\,MeV, TALYS/TENDL both reproduce the present work, as well as earlier measurements, suggesting that angular momentum transfer in the pre-equilibrium regime is being well-modeled, but that the total feeding of the \ce{^{44}Sc} channel is  underestimated. 
A similar argument holds for EMPIRE, which reproduces the isomer branching  up to 35\,MeV.
However, CoH fails to reproduce either the channel magnitude or the isomer ratio,
% , suggesting a more fundamental issue with the modeling of this channel. 
\ce{^{47}Sc} presents a very opposed situation, despite an abundance of reaction data and strong feeding of the channel.
All codes fail to reproduce either the shape or magnitude of this channel, with only CoH able to predict the compound peak,  and failing to model the pre-equilibrium tail.
As a cumulative reaction channel, it is unclear whether this failure arises from modeling of any \ce{^{47}Ca} decay precursors, or the competition between  \ce{^{48}Ti}(p,20)\ce{^{47}Sc} / \ce{^{49}Ti}(p,2pn)\ce{^{47}Sc} / \ce{^{50}Ti}(p,$\alpha$)\ce{^{47}Sc} channels. 
Modeling of \ce{^{48}Sc} is lacking, with only TALYS/TENDL matching the shape of the excitation, and all codes failing to reproduce the magnitude of the channel.

>>>>

        \subfigimg[width=0.485\textwidth]{b)}{./figures/after_minimization_plot_alt.pdf}{50}
         %         \refstepcounter{subfigure}
         \label{fig:fe_after_minimization}
   \hspace{-5pt}}%
    \caption{Proton fluence at various positions in both the 55\,MeV and 25\,MeV target stacks as determined by the Ti and Cu monitor foils before (left) and after (right) variance minimization. Open data points represent the 25\,MeV stack, and filled data points represent the 55\,MeV stack. The abrupt change in the post-minimization value at the energies where the two stacks overlap can be attributed to the relatively large energy straggle at the back of the high energy stack.}  
%     Results of variance minimization through increasing the effective areal density of the  aluminum degraders by 4.43\% (55\,MeV stack) and Kapton tape by 5.69\% (25\,MeV stack). A noticeable reduction of variance in measured proton fluence is seen,  particularly at the  rear stack positions.  Open data points represent the 25\,MeV stack, and filled data points represent the 55\,MeV stack.} 
     \label{fig:fe_variance_mins}
\end{figure*}

@@

In addition to the \ce{^{nat}Fe}(p,x)\ce{^{51,52}Mn} measurements, this experiment has also yielded production cross section  measurements of  a number of additional  emerging radionuclides with medical applications,
including the non-standard positron emitter 
% \ce{^{44}Sc}\,\cite{Muller2013,Filosofov2010,Qaim2011}
%\,\cite{Qaim2011,Qaim201731,Kolsky1998,mausner1995evaluation}.
\ce{^{55}Co}\,\cite{Thisgaard2011,Zaman1996,Hermanne2000a}.
% \ce{^{61}Ni}\,\cite{PMID:7632762,zweit1996medium,Graves2016,Rosch2014}, 
% \ce{^{61}Cu}\,\cite{Szelecsenyi2005a,Fukumura2004}
% \ce{^{64}Cu}\,\cite{Lewis2003,Bandari2014,mp500671j,Szelecsenyi1993,Aslam2009,Hilgers2003,Szelecsenyi2005,Voyles2017},
% \ce{^{86}Y}\,\cite{Valdovinos2017,Nickles2003,Qaim2008,QaimSyedM2011,Rosch1993,doi:10.1139/v67-193,levkovski1991cross,Johnson2015,Singh2013,Kiselev1974,Kandil2009}, 
% \ce{^{89}Zr}\,\cite{Verel2003,Dijkers2009,Dijkers2010,PhysRevC.38.1624,Omara2009},  
% \ce{^{90}Nb}\,\cite{Busse2002,Radchenko2012},  
% the $\beta^-$-therapy agent  \ce{^{64}Cu},  
% and the $\beta^-$-therapeutic agent 
% \ce{^{47}Sc}\,\cite{Muller2014,Deilami-nezhad2016}.
% and the Auger-therapy agent \ce{^{82\text{m}}Rb}\,\cite{Kovacs1991,Titarenko2011}. 
Production of this radionuclide offers no major advantages over established pathways, with the  lower yield and radioisotopic purity failing to justify the convenience of natural targets  via   \ce{^{nat}Fe}(p,x).
The one potential exception to this is the production of \ce{^{58m}Co}, a potent agent for Auger electron-based targeted therapy\,\cite{Thisgaard2011a,Valdovinos2017b,Thisgaard2014a}.
While ingrowth of the long-lived \ce{^{58g}Co} ($t_{1/2}$ = 70.86(6) d\,\cite{Nesaraja2010}) is unavoidable, lowering the  co-production of \ce{^{58g}Co} is necessary to minimize patient dose.
The \ce{^{nat}Fe}(p,x)\ce{^{58m}Co} pathway shows a clear \enquote{peak} in the \ce{^{58m}Co}/\ce{^{58g}Co} branching ratio for approximately 15--30\,MeV protons, which might have translational implications if Auger electron therapy becomes more clinically prevalent.

@@

% Perhaps due to the abundance of reaction data available, 
The modeling of these channels is markedly improved  in comparison to the \ce{^{nat}Fe}(p,x) channels discussed previously.
For \ce{^{44m}Sc}, 
% the shape of the excitation function is well-modeled by EMPIRE, CoH, TALYS, and TENDL, though 
all  codes place the compound peak approximately 4\,MeV lower than observed, and EMPIRE overestimates the magnitude of this peak, while TALYS, TENDL, and CoH significantly underestimate it.
Notably, the pre-equilibrium tail and transition towards a second peak near 65\,MeV is well-modeled by TALYS/TENDL, but significantly underestimated by EMPIRE and CoH.
The same modeling trend is observed for \ce{^{44m}Sc}, 
% though no judgment can be made for the pre-equilibrium tail, due to a paucity of data above 50\,MeV.
and reflected in the measured isomer branching ratios for \ce{^{44}Sc}, seen in \autoref{fig:44Sc_IBR}.
Above 23\,MeV, TALYS/TENDL both reproduce the present work, as well as earlier measurements, suggesting that angular momentum transfer in the pre-equilibrium regime is being well-modeled, but that the total feeding of the \ce{^{44}Sc} channel is  underestimated. 
A similar argument holds for EMPIRE, which reproduces the isomer branching  up to 35\,MeV.
However, CoH fails to reproduce either the channel magnitude or the isomer ratio,
% , suggesting a more fundamental issue with the modeling of this channel. 
\ce{^{47}Sc} presents a very opposed situation, despite an abundance of reaction data and strong feeding of the channel.
All codes fail to reproduce either the shape or magnitude of this channel, with only CoH able to predict the compound peak,  and failing to model the pre-equilibrium tail.
As a cumulative reaction channel, it is unclear whether this failure arises from modeling of any \ce{^{47}Ca} decay precursors, or the competition between  \ce{^{48}Ti}(p,20)\ce{^{47}Sc} / \ce{^{49}Ti}(p,2pn)\ce{^{47}Sc} / \ce{^{50}Ti}(p,$\alpha$)\ce{^{47}Sc} channels. 
Modeling of \ce{^{48}Sc} is lacking, with only TALYS/TENDL matching the shape of the excitation, and all codes failing to reproduce the magnitude of the channel.
